Writing Trash Bin

### 2024-08-08 paper.qmd
added notes
wrote future work

@@

# Future work
This paper has identified gaps in the uncertainty visualisation literature that could be filled to progress the field.

*Each new development should be accompanied by a mathematical definition of the uncertainty being addressed.* Ideally, a mathematically definition of uncertainty that allows us to combine these components would be developed, but in the absence of that, authors should be more specific about what aspect of "uncertainty" they are covering with their visualisation.

*The concept of uncertainty should be formalised within the grammar of graphics.* This formalisation would allow uncertainty visualisation authors to have a clear understanding of what is or is not an uncertainty visualisation. Additionally placing uncertainty visualisation in the framework that is used to understand existing information visualisation research would help authors understand when existing methods can be used to explain their results. incorporating uncertainty into the grammar of graphics will also give a more precise concept of the information contained within a plot. Other fields of science employ marginal changes when designing experiments to ensure it is well understood *what* aspect of their experiment is contributing to their results, and a better sense of what "marginal" is in the case of uncertainty visualisation would greatly help the field. (*XXX Is data pipeline connected with the grammar of graphics? Should this be a recommendation?*)

*Experimental practices on uncertainty visualisation need to be standardised.* If we are going to consider uncertainty as noise, not signal, there needs to be a way to identify this signal suppression in an experimental design. As the literature currently exists, there is no way to combine papers to get a meaningful sense of how uncertainty information is understood by a viewer. There is also the possibility that uncertainty visualisation evaluations will need to swap to a qualitative methodology where participants are allowed to freely comment on what they notice in graphics until we establish how the existence of noise can be observed.

If an uncertainty visualisation researcher would prefer to perform experiments rather than formalise methods, there are options there too. It would be interesting to know if any perceptual tasks that can be mapped to two different visual tasks condense into a single dimension when looking for overarching signal in a plot. Alternatively, the task dependency many authors in uncertainty visualisation mention would be a useful direction to consider. It is clear that the the number of potential tasks that can be performed on a visualisation increases with with the number of observations. A single observation is limited to value extraction, two observations can be compared, multiple observations allow for shapes or global statistics to be extracted. The interaction between sample size and task is of particular interest to the uncertainty visualisation community, as uncertainty can be expressed through multiple observations using a sample, or through a single value using an error. Of course, this is limited by the fact that there also isn't a definition for what is a "task" and given the mess created by the lack of formalisation in uncertainty visualisation, it may be wise to formalise that concept before performing these experiments. @Amar2005 suggested a taxonomy for information visualisation based on the types of tasks we use visualisations for and suggest 10 "analytical primitives" that we can then map to visualisations, which could be a good starting point. Regardless, these are directions of research would be fruitful to the uncertainty visualisation community even if it appears on the surface to be research that is only beneficial to the "normal" visualisation community. (*XXX Not sure what this paragraph is recommending?*)

>>>>

## Example Data
Throughout this review, we will be looking at

- add map that is just outline
- include function used to design temperature

@@

# Future work
This paper has identified gaps in the uncertainty visualisation literature that could be filled to progress the field. We formalized the uncertainty visualisation problem, and in doing so highlighted an untouched area of uncertainty visualisation research.

*Experimental practices on uncertainty visualisation need to be standardised.* Uncertainty visualisations for decision making treat uncertainty as signal, while visualisations for signal-suppression treat uncertainty as noise. As the literature currently exists, there is no way to combine papers to get a meaningful sense of how uncertainty information is understood by a viewer. Researchers need to ensure that when they identify the motivation behind their visualisation technique, and that their evaluation methods match the motivations of the paper. Additionally *evaluation methods that evaluate uncertainty as noise need to be developed.*

*Experimenters should consider evaluating visual aesthetics on how well they suppress information in a graphic.* Research into separability and integrability is of particular interest to uncertainty visualisation, as it allows interference from the uncertainty variable. When designing experiments, authors often choose aesthetics that are visually distinguishable, uncertainty visualisation authors should consider doing the opposite.

*Software that allows users to easily perform signal suppression should be developed.* Existing uncertainty visualisation methods view a distribution as its own object and there are no software options for the "an uncertainty visualisation is a function of a visualisation" philosophy.

### 2024-08-08 writingdumpster.qmd
wrote future work

# Removed Sections
The beauty of visualisation is that it *tells* us what we should be concerned about in our analysis. This aspect disappears the second we ask a direct question about our visualisation.

>>>>

# Removed Sections
@Amar2005 suggested a taxonomy for information visualisation based on the types of tasks we use visualisations for and suggest 10 "analytical primitives" that we can then map to visualisations, which could be a good starting point.

The beauty of visualisation is that it *tells* us what we should be concerned about in our analysis. This aspect disappears the second we ask a direct question about our visualisation.
